Applications of Technology and Large Data in Statistics Education and Statistical Graphics

### 2015-05-29 Body/LitReview/LitReview.Rnw
Future Work / Submissions slide

There are arguments to be made against the use of experiments in educational studies. \citet{Cook2002} argues that experimental logic strongly supports causal conclusions but outlines several practical reasons why he believes they are not used in education.  He argues that there are often insurmountable problems with properly implementing experiments in schools, results tend to trade external validity for causal isolation, and that often observational studies may establish strong enough associations to make the necessary policy decisions. There are also those who are more philosophically opposed to experiments in education. \citet{Howe2004} argues that the quantitative methods used in experimentation are not capable of measuring student learning in any meaningful way and that qualitative methods are the only appropriate approach to assess learning. Aside from his astoundingly imprecise and inept criticism of the experimental methodologies, his assertion that we cannot quantify understanding or learning is fundmentally incorrect. Educators -- perhaps imperfectly -- regularly quantify student knowledge through the grading of assessments and substantial research has been done on tools designed to measure student learning in statistics.

>>>>

There are arguments to be made against the use of experiments in educational studies. \citet{Cook2002} argues that experimental logic strongly supports causal conclusions but outlines several practical reasons why he believes they are not used in education.  He argues that there are often insurmountable problems with properly implementing experiments in schools, results tend to trade external validity for causal isolation, and that often observational studies may establish strong enough associations to make the necessary policy decisions. There are also those who are more philosophically opposed to experiments in education. \citet{Howe2004} argues that the quantitative methods used in experimentation are not capable of measuring student learning in any meaningful way and that qualitative methods are the only appropriate approach to assess learning. Aside from his astoundingly imprecise and inept criticism of the experimental methodologies, his assertion that we cannot quantify understanding or learning is fundamentally incorrect. Educators -- perhaps imperfectly -- regularly quantify student knowledge through the grading of assessments and substantial research has been done on tools designed to measure student learning in statistics.

### 2015-05-29 DefenseSlides/DefenseSlidesCommitteeHour.Rnw
Future Work / Submissions slide

>>>>

\begin{frame}
    \frametitle{Future Work for Thesis Components} 
Literature Review
  \begin{itemize}
    \item Section 2 to be submitted to JSE as review of technology in statistics education
  \end{itemize}

Statistical Inference Curriculum Comparison Study
  \begin{itemize}
    \item Accepted pending revision by TISE
    \item Awaiting results in second round of reviews
  \end{itemize}

Shiny Database Sampler
  \begin{itemize}
    \item Move application to more reliable R Server
    \item Manuscript to be submitted to TISE or SERJ
  \end{itemize}

Loss in Binned Scatterplots
  \begin{itemize}
    \item Manuscript to be submitted to JCGS
  \end{itemize}
